---
title: "week9"
author: "Charlene Zhang"
date: "3/14/2020"
output: pdf_document
params:
    output_dir: "../output"
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "../output") })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("/Users/zhan5449/Google Drive/Data Science/Week 9/Week-9-Project")
```

# Libraries
```{r,include=FALSE}
library(tidyverse)
library(lubridate)
```

# Data Import
  + Read in Data from Week3 as a Tibble
  + Converted timeStart and timeEnd to POSIX variables
  + Converted gender and condition to factor variables
  + Created mean scores of Q1 to Q5 and means scores for Q6 to Q10 for subsequent visualization and analysis
```{r}
week9_tbl <- read_csv("../data/week3.csv") %>%
  mutate(timeStart=ymd_hms(timeStart),
         timeEnd=ymd_hms(timeEnd),
         gender=factor(gender,levels=c("M","F"),labels=c("Male","Female")),
         condition=factor(condition,levels=c("A","B","C"),labels=c("Block A","Block B","Control")),
         Q1_Q5=rowMeans(select(.,q1:q5),na.rm=TRUE),
         Q6_Q10=rowMeans(select(.,q6:q10),na.rm=TRUE)) 
```

# Visualization
```{r,echo=FALSE}
ggplot(week9_tbl,aes(x=Q1_Q5,y=Q6_Q10))+
  geom_point()+
  geom_smooth(method="lm",se=F)+
  labs(x="Mean scores of Q1 to Q5",
       y="Mean scores of Q6 to Q10",
       title="Scatterplot between the Q1-Q5 mean and the Q6-Q10 mean")
```

This is a scatterplot that shows the relationshiip between mean scores of Q1-Q5 and mean scores of Q6-Q10, with an OLS regression line. 

# Analysis
```{r}
corr <- cor.test(week9_tbl$Q1_Q5,week9_tbl$Q6_Q10)$estimate 
p <- cor.test(week9_tbl$Q1_Q5,week9_tbl$Q6_Q10)$`p.value` 
```

The correlation was `r corr` (p = `r p`), which is not statistically significant. 